Cyclone: Fault Tolerance Middleware for NVM Clusters

### 2016-05-10 paper/paper.tex
Updates to paper.

\section{Example Applications}
\label{sec:examples}

\section{Evauation}

\subsection{Baseline}

\subsection{Configuration Management}

\subsection{Transaction Processing}

\subsection{Network Function Virtualization}

>>>>

\section{Example Application}
\label{sec:examples}
We now demonstrate how Cyclone can be used in practise by putting together an
example of a linearizable set of counters. The problem is to construct a sparse
set of counters indexed by a 64 bit key and support \emph{linearizable}
increment, decrement and an atomic set increment. The atomic set increment takes
as input a set of counter indexes and their current value and atomically
increments the counters from the the given values.

\begin{figure*}
\begin{tabular}{cc}    
\begin{minipage}{0.5\textwidth}  
{ \scriptsize
\begin{verbatim}
bool is_stable(uint64_t value)
{
  if(value is even) {
    return true
  }
  else {
    return false
  }
}

Get(uint64_t index)
{
  if(not is_stable(counters[index]) {
    return EUNSTABLE
  }
  else {
    return counters[index]
  }
}

Increment(uint64_t index)
{
  if(not is_stable(counters[index]) {
    return EUNSTABLE
  }
  else {
    counters[index] = counters[index] + 2
    return SUCCESS
  }
}
\end{verbatim}
}
\end{minipage} &
\begin{minipage}{0.5\textwidth}  
{ \scriptsize
\begin{verbatim}
Prepare(uint64_t index, uint64_t value, bool success)
{
  if(counters[index] == value) {
    success = success AND TRUE
  }
  else {
    success = success AND FALSE
  }
  // Make unstable
  counters[index] = counters[index] + 1
}

Commit(uint64_t index, bool success)
{
  if(success == TRUE) {
    // Update
    counters[index] = counters[index] + 1
  }
  else {
    // Rollback
    counters[index] = counters[index] - 1
  }
}

AtomicIncrementSet(uint64_t indices[],
                   uint64_t pre_values[],
                   int count)
{
  bool success = TRUE
  for i = 1 to count
    success =
      success AND
        Prepare(indices[i],
                pre_values[i],
                success)
  for i = 1 to count
    Commit(indices[i], success)       
}
\end{verbatim}
}
\end{minipage}
\end{tabular}
\caption{Counter Set}
\label{fig:counter_set}
\end{figure*}
